Phenomenological Robotics

### 2011-12-09 draft.tex
Wrote about the failure of the computation hypothesis on everyday coping.

>>>>

% 1.A. "Failure" of the computational hypothesis on everyday coping (being in
% the world is more basic than thinking).
% (Source: \cite{dreyfus07}.)

He points out that the pioneers in GOFAI learned, directly or indirectly, from
the philosophers. Hobbes' claim that reasoning was calculating and Descartes'
mental representations, among others, are cited as examples. At the same time,
he states that the critical insights formulated by existentialist philosophers,
such as Heidegger and Merleau-Ponty, were a sign that their enterprise was
comdemned to failure.

He criticizes Newell and Simon's claim that the mind could be understood as a
\emph{physical symbol system}, where streams of neuron pulses would be used as
symbols to represent the external world. Dreyfus points out that

\begin{quotation}
  Heidegger's important insight is not that, when we solve problems, we
  sometimes make use of representational equipment outside our bodies, but that
  \emph{being-in-the-world} is more basic than \emph{thinking} and solving
  problems; that it is not representational at all.
\end{quotation}
